TIM: Tree Imaging Machine for low-cost digital images of tree cores and cookies

### 2025-03-19 docs/writing/paper.tex
Mentioning adding encoders for more accurate movement

To reduce motion blur in the images, the range of $\boldsymbol{Z_{\text{samples}}}$ is traversed at constant velocity and images are captured without stopping. 
Decoupling the auxiliary camera control from the G-code commands to control the machine has shown to improve speed and decrease vibrational effects from acceleration and deceleration \citep{propst_time_2025}.
This is a variation of the standard approach used in 3D printing and Computer Numerical Control (CNC) machine control.

@@

Our implementation of focusing images could be improved with the aid of additional sensors. Much of the imaging time of samples is the result of taking a vertical stack of images to obtain one in focus image. In advanced microscopy applications, it is common to see supplemental sensors used to measure the distance between the subject and lens.
Adding sensor support and a control loop to focus images could significantly reduce sampling time on the scale of an order of magnitude.

>>>>

To reduce motion blur in the images, the range of $\boldsymbol{Z_{\text{samples}}}$ is traversed at constant velocity and images are captured without stopping. 
Decoupling the auxiliary camera control from the G-code commands to control the machine has shown to decrease digitization time and decrease vibrational effects from acceleration and deceleration \citep{propst_time_2025}.
This is a variation of the standard approach used in 3D printing and Computer Numerical Control (CNC) machine control.

@@

Our implementation of focusing images could be improved with the aid of additional sensors. Much of the imaging time of samples is the result of taking a vertical stack of images to obtain one in focus image. 
In advanced microscopy applications, it is common to see supplemental sensors used to measure the distance between the subject and lens.
Adding sensor support and a control loop to focus images could significantly reduce sampling time on the scale of an order of magnitude. 
Using rotary encoders on each of the motors controlling the X and Y movement would be a welcomed addition---this would greatly increase the 
accuracy of the the location of the camera on the work plane.
